Title

### 2013-03-08 inc/extension/external_forces/practical.tex
included a summary of RF cav resultant M/F terms

@@

To specify the physical region of influence of the lenses, it is convenient to redefine $M_{i}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{i}	\to M_{i} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{\smallzero} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures, as illustrated by $1 \frac{1}{2}$-cell RF photo-gun designs.\cite{mcdonald_design_1988}
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

% excluded example section from JAP paper as it will need new graphics

>>>>

The mathematical formalism developed in Section \ref{sec:external_forces} is only an abstract mechanism for including external forces.
To model electron pulses traveling through realistic electron microcope columns, these abstract mechanisms must be developed further to properly describe each specific electron-optical element.
In the following section I demonstrate concrete applications of the extended AG model, including magnetic lenses, radio-frequency (RF) cavities (useful for both pulse compression and acceleration %TODO refs
) and DC acceleration regions (i.e. electron gun dynamics).

@@

Of course, physical electron-optical elements occupy only a finite space in the column, and thus their influence on the pulse should be limited to a region near the element itself.
To localize the mathematical result shown in Section \ref{sec:external_forces}, it is convenient to redefine $M_{i}$ to include a super-Gaussian envelope in $z^{\prime}$, the position of the peak of the pulse in the lab frame;
\begin{equation} \label{eq:reg_of_influence}
  M_{i}	\to M_{i} \exp \left [ - \left (  \frac{ z^{\prime} - z_{lens}^{\prime} }{ L_{lens} / 2 } \right )^{ 2 n } \right ] \text{ ,}
\end{equation}
where $z_{lens}^{\prime}$ is the position of the center of the lens, $L_{lens}$ is the length of the lens and $n$ is the super-Gaussian order parameter.
The order parameter defines the ``sharpness'' of the edge of the region of influence with integer values ranging from 1 (a simple Gaussian) through $\infty$ (a top-hat).
We connect $z^{\prime}$ to $t$ through $ v_{\smallzero} $; the kinetic equations are simply defined for the position of the peak of the pulse.

@@

The two main effects contributing to the transverse lens of a $\text{TM}_{010}$-mode RF cavity, its magnetic field component and electric fringe field aperture effects, may also be included within the linear force approximation.
The azimuthal magnetic component of the resonant mode oscillates 90$^{\circ}$ out of phase with the electric component and with a $\operatorname{ J_{1} }$ Bessel radial form; i.e., $ \operatorname{ J_{1} }( k r / a ) \sim k r / a $ for small $r$.
Symmetry and Gauss' Law dictate that in the vicinity of the axial center of the entrance and exit apertures of the RF cavity there exists a radial component of the oscillating electric field determined by $ E_{r} = -\left ( r / 2 \right ) \left ( \partial E_{z} / \partial z \right )_{r=0} $,\cite{kim_rf_1989} where the form of the axial electric field for $\text{TM}_{010}$ oscillation (\ref{eq:RF_Efield}) implies that, in the context of this analysis, its axial gradient is solely dependent upon the envelope function for the RF cavity (\ref{eq:reg_of_influence}).
In practice, of course, the exact form of $E_{r}(z)$ is strongly tied to the size and shape of the RF cavity apertures (see for example $1 \frac{1}{2}$-cell RF photo-gun designs \cite{mcdonald_design_1988}). 
For the case of an evacuated cavity, these two contributions result in a net force,
\begin{equation} \label{eq:RF_Force_r}
  \boldsymbol{F}_{ r , RF } = e E_{0} \left [ 
    \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] r \hat{\operatorname{ \boldsymbol{r} }} \text{.}
\end{equation}
In obtaining \ref{eq:RF_Force_r}, which is also of the form for use in \ref{eq:linear_force}, we have again used an arbitrary super-Gaussian of order $n$ as a region of influence envelope (see \ref{eq:reg_of_influence}) with $L_{RF} \equiv d$, the RF cavity length.
For the examples shown below under the pulse compression conditions ($\phi = 0$ when the pulse is at $z^{\prime} = 0$), both effects are defocusing for the electron pulse and the magnetic contribution is smaller than the transverse lenses associated with the RF cavity apertures when $ d = \pi v_{\smallzero} / \Omega $,\cite{kim_rf_1989} even though its magnitude is maximized for $\phi = 0$.
Other effects, such as magnetic fringe field aperture effects, could also be included, but are significantly weaker.

To summarize, the additional terms are which are added to model internal pulse dynamics arising from a single RF cavity are
\begin{gather}
  M_{z}^{RF} = \left [ \frac{ e \Omega E_{0} }{ v_{\smallzero} } \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \\
  \begin{aligned}
  M_{\smallT}^{RF} = & e E_{0} \left [ \frac{ v_{\smallzero} \Omega }{c^{2}} \cos \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) + \frac{2 n}{d} \left ( \frac{z^{\prime} - z^{\prime}_{RF}}{d / 2} \right )^{2 n - 1} \right. \\ \times & \left. \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right )
   \right ] \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ]
  \end{aligned}
\end{gather}
Additionally, an acceleration force term
\begin{equation}
  F_{z}^{RF} = E_{0} \sin \left ( \frac{ \Omega z^{\prime} }{ v_{\smallzero} } + \phi \right ) \exp \left [ - \left (  \frac{ z^{\prime} - z_{RF}^{\prime} }{ L_{RF} / 2 } \right )^{ 2 } \right ] \, \text{,}
\end{equation}
which originates from the leading term in \ref{eq:RF_Efield_approx}, should be added to the dynamics of the motion of the overall pulse.
% excluded example section from JAP paper as it will need new graphics

### 2013-03-08 inc/extension/implementation/implementation.tex
tweak implementation section
included a summary of RF cav resultant M/F terms

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicy benefit added by that dependency is marked.
Usefully, it also comes with a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this model to generate the pulse's $z$ direction initial conditions.

>>>>

Additionally, a development version of the bin model presented in Section \ref{sec:bin_model} is available at \url{https://github.com/jberger/Physics-Photoemission}.
Once I am sufficently confident in its implementation, and more importantly its voracity, I intend to release it to the CPAN as well, most likely under the name \verb!Physics::Photoemission!.
This module depends on the much larger Perl project PDL (\url{http://pdl.perl.org}), a matrix-oriented numerical library, making it slightly more difficult to install, however the speed and implementational simplicy benefit added by that dependency is marked.

Of particular interest to users of \verb!Physics::UEMColumn!, \verb!Physics::Photoemission! also includes a subclass of \verb!Physics::UEMColumn::Photoemission! which uses this binning model to generate the pulse's $z$ direction initial conditions.
